---
title: "Testing recommender system algorithm"
author: "Harpo"
date: "11/4/2016"
output: 
  html_document: 
    fig_height: 5
    fig_width: 12
    highlight: espresso
    theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressMessages(library(caret))
suppressMessages(library(dplyr))
suppressMessages(library(doMC))
suppressMessages(library(randomForest))
registerDoMC(cores=4)
```
## Datasets

3 Datasets are used:

1. Dataset 22
2. Dataset 45
3. Dataset 87

```{r}
setwd("/home/harpo/Dropbox/ongoing-work/git-repos/labeling-datasets/")
#lees el archivo
datasetfull=read.csv(file="./data/characteristic_vector_22_all.txt",header=F)
datasetfull=cbind(rep(22),datasetfull)
names(datasetfull)<-c("id","sp","wp","wnp","snp","ds","dm","dl","ss","sm","sl","length","class","subclass")
dataset=read.csv(file="./data/characteristic_vector_45_all.txt",header=F)
dataset=cbind(rep(45),dataset)
names(dataset)=c("id","sp","wp","wnp","snp","ds","dm","dl","ss","sm","sl","length","class","subclass")
datasetfull=rbind(datasetfull,dataset)
dataset=read.csv(file="./data/characteristic_vector_87_all.txt",header=F)
dataset=cbind(rep(87),dataset)
names(dataset)=c("id","sp","wp","wnp","snp","ds","dm","dl","ss","sm","sl","length","class","subclass")
datasetfull=rbind(datasetfull,dataset)
datasetfull$class=factor(datasetfull$class)
datasetfull$subclass=factor(datasetfull$subclass)
datasetfull$id=factor(datasetfull$id)
```

## Feature engineering 

For a given Stratosphere connection $N$:
we create a feature vector $V(X_1,X_2,...,X_{10})$ where each $X_i$ calculate a value for the following features in $F(SP,WP,WNP,SNP,DS,DM,DL,SS,SL,SM)$. Then each $X_i=\frac{\sum(letters\in F_i) * 100}{|N|}/100$. The following python code is used for generating the feautres.

##Correlation analisis of the new features

```{r, fig.height=8, fig.width=12}
splom(~datasetfull[,2:12],data=datasetfull,
        groups=datasetfull$class,
        diag.panel = function(x, ...){
          yrng <- current.panel.limits()$ylim
          d <- density(x, na.rm=TRUE)
          d$y <- with(d, yrng[1] + 0.95 * diff(yrng) * y / max(y) )
          panel.lines(d)
          diag.panel.splom(x,...)
        },cex=0.5,xlab="",ylab="",auto.key = TRUE,cex.labels=0.1,pscales = 0,alpha=0.5,varname.cex=0.8
  )
```


## Class and subclass Distribution
```{r, fig.height=8, fig.width=10, warning=FALSE}
histogram(~class|id,datasetfull)
histogram(~subclass|id,data=datasetfull,groups=class,col=c("skyblue","pink"),scales=list(x=list(rot=90),cex=0.7),layout=c(1,1),auto.key = F)
```

## length Distribution

```{r}
densityplot(~length|id,data=datasetfull,groups=class,auto.key=T,scales=list(x=list(rot=45,relation='free',log=10),y=list(relation='free')),layout=c(1,1),breaks=5)

```
```{r, fig.height=8, fig.width=10}
barchart(length~factor(subclass)|id,groups=class,data=datasetfull,auto.key=T,scales=list(x=list(rot=90),y=list(relation='free'),cex=0.70),layout=c(1,1))

```


## Setting dataset 22 as training set using RandomOversampling
```{r}
#datasetfull=datasetfull %>% filter(length>5)

train=datasetfull %>% filter(id==22) %>% filter(length>5)
train <- upSample(x = train,  y = train$subclass, yname="class")     
# removing dataset Id,subclass, and class.1 (added by upSample)
train <- train[,-c(1,14,15)]
```


## Random Forest Tuning over 10-fold cross validation
```{r}
ctrl_fast <- trainControl(method="cv", 
                     repeats=1,
                     number=2, 
                     summaryFunction=twoClassSummary,
                     verboseIter=T,
                     classProbs=TRUE,
                     allowParallel = TRUE)   
# Random Forest
rfFit <- train(class ~ .,
               data = train,
               metric="ROC",
               method = "rf",
               trControl = ctrl_fast)
```

### Final Model
```{r}
rfFit
rfFit$finalModel
```

## Test on Dataset 45

```{r}
test45=datasetfull %>% filter(id==45)
# removing dataset Id and subclass
test45 <- test45[,-c(1,14)]
predsrfprobs=predict(rfFit,test45,type='prob')
predsrf=ifelse(predsrfprobs$Botnet >0.5,'Botnet','Normal')
confusionMatrix(predsrf,test45$class)
```

##  Incorrectly Classified Connections
### False Positive

```{r}
subclasses=cbind(datasetfull %>% filter(id==45) %>% select(subclass,class),predsrf,predsrfprobs)
fp=subclasses %>% filter(class=='Normal' & predsrf=='Botnet')# %>% select(subclass,Botnet,Normal)
histogram(~subclass|predsrf,data=fp,scales=list(x=list(rot=45)),type='count')
```

### False Negative
```{r}
fn=subclasses %>% filter(class=='Botnet' & predsrf=='Normal') #%>% select(subclass,Botnet,Normal)
histogram(~subclass|predsrf,data=fn,scales=list(x=list(rot=45)),type='count',col='orange')
```

## Test on Dataset 87
```{r, fig.height=3, fig.width=8}
test87=datasetfull %>% filter(id==87)
# removing dataset Id and subclass
test87 <- test87[,-c(1,14)]
predsrfprobs=predict(rfFit,test87,type='prob')
bwplot(~Botnet,data=predsrfprobs)
bwplot(~Normal,data=predsrfprobs)
predsrf=ifelse(predsrfprobs$Botnet >0.5,'Botnet','Normal')
print(caret::confusionMatrix(predsrf,test87$class))

```

##  Incorrectly Classified Connections
### False Positive
```{r}
subclasses=cbind(datasetfull %>% filter(id==87) %>% select(subclass,class),predsrf,predsrfprobs)
fp=subclasses %>% filter(class=='Normal' & predsrf=='Botnet')# %>% select(subclass,Botnet,Normal)
histogram(~subclass|predsrf,data=fp,scales=list(x=list(rot=45)),type='count')
```

### False Negative
```{r}
fn=subclasses %>% filter(class=='Botnet' & predsrf=='Normal') #%>% select(subclass,Botnet,Normal)
histogram(~subclass|predsrf,data=fn,scales=list(x=list(rot=45)),type='count',col='orange')
```